Tables and Figures - Supplement A, B and C

### 2020-03-27 code/04_tables.rmd
Updated Figures to be APA consistent, minor table fix

## Table 1
### Variation in observed effect sizes as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
ma <- c("I: $\\rho_{xy} = 0.0$", "II: $\\rho_{xy} = 0.3$", "III: $\\rho_{xy} = 0.5$")

rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
devs <- apply(rooted_relabilities, 2, sd)
table1 <- data.frame(ma, t(rooted_relabilities), devs)

table1 %>% knitr::kable(booktabs = T, col.names = c("Meta-Analysis", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  add_header_above(c(" " = 1, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
  add_header_above(c(" " = 1, "Observed Effect Sizes" = 3))

#alternative inversed table 1
# table1b <- t(table1)[2:5,]
# studies <- c("Study 1: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "Study 2: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "Study 3: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)")
# table1b <- cbind(studies, table1b)
# rownames(table1b) <- NULL
# 
# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\rho_{xy} = 0$", "II: $\\rho_{xy} = .3$", "III: $\\rho_{xy} = .5$"), escape = FALSE, digits = 2) %>% 
#   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
#   add_header_above(c(" " = 1, "Observed effect sizes" = 3)) %>% 
#   row_spec(3, hline_after = TRUE)
```
*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$ when within study sample size is infinite. SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06

@@

            "Hostility priming; Independent two-group experiment. Participants descrambled sentences, either 20% or 80% were hostile, then rated ambiguous behavior.", #RRR9

@@

summary.table %>% knitr::kable(booktabs = TRUE,
                               digits = 0,
                               linesep = "\\addlinespace",
                               longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 7) %>%
  column_spec(2, width = "7em") %>% #specify width of paper column 
  column_spec(7, width = "16em") %>% 
  column_spec(8, width = "30em") %>% 
  landscape()
```
**Note:** For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. N = Participants used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, K (US) = no. primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"

## Table 3
### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE, results = 'hide'}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

het$effect <- gsub("&", "\\\\&", het$effect)
```

@@

het %>% knitr::kable(align = "c", longtable = TRUE, booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"), font_size = 7) %>% #comment out if outputting html file
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. All ML2 meta-analyses with effect type 'r' except 'Moral foundations' and 'Social Value Orientation' were transformed to correlations from a variety of effect sizes. RP = Replication Project, K = no. primary studies, $\\\\hat\\\\tau$ = between studies standard deviation, CI = confidence intervals. Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large
heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06" ,
           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% landscape()
```

>>>>

## Table 1
### Variation in observed effect sizes as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
ma <- c("I", "II", "III")

rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
devs <- apply(rooted_relabilities, 2, sd)
table1 <- data.frame(ma, rho, t(rooted_relabilities), devs)

table1 %>% knitr::kable(booktabs = T, col.names = c("Meta-Analysis", "$\\rho_{xy}$", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  add_header_above(c(" " = 2, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
  add_header_above(c(" " = 2, "Observed Effect Sizes" = 3))

#alternative inversed table 1
# table1b <- t(table1)[2:5,]
# studies <- c("Study 1: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "Study 2: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "Study 3: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)")
# table1b <- cbind(studies, table1b)
# rownames(table1b) <- NULL
# 
# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\rho_{xy} = 0$", "II: $\\rho_{xy} = .3$", "III: $\\rho_{xy} = .5$"), escape = FALSE, digits = 2) %>% 
#   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
#   add_header_above(c(" " = 1, "Observed effect sizes" = 3)) %>% 
#   row_spec(3, hline_after = TRUE)
```
*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$ when within study sample size is infinite. SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes. Code to reproduce table: osf.io/gtfjn/

@@

            "Hostility priming; Independent two-group experiment with two outcome variables. Participants descrambled sentences, either 20% or 80% were hostile, then rated an individual and a list of ambiguous behaviors on perceived hostility.", #RRR9

@@

summary.table %>% knitr::kable(booktabs = TRUE,
                               digits = 0,
                               linesep = "\\addlinespace",
                               longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 7) %>%
  column_spec(2, width = "7em") %>% #specify width of paper column 
  column_spec(7, width = "16em") %>% 
  column_spec(8, width = "30em") %>% 
  landscape()
```
**Note:** For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. N = Participants used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, K (US) = no. primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report. Code to reproduce table: osf.io/gtfjn/

## Table 3
### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, results = 'hide'}
#library(metafor) 
#library(dplyr)
#library(purrr)

@@

het$effect <- gsub("&", "\\\\&", het$effect)

#highlight the effects in Figure 3
fig3_smds <- unique(dat$effect[dat$outcomes1_2 == "mean _ SD"]) 
fig3_logor <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales', #ML1 (OR2d)
                "Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2", #ML2
                "Verbal overshadowing 1", "Verbal overshadowing 2") #RRR1

het$effect <- ifelse(het$effect %in% fig3_smds, paste0(het$effect, footnote_marker_symbol(1)), het$effect)
het$effect <- ifelse(het$effect %in% fig3_logor, paste0(het$effect, footnote_marker_symbol(2)), het$effect)

```

@@

het %>% knitr::kable(longtable = TRUE, booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>%
  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>%
  kable_styling(latex_options = c("scale_down", "repeat_header"), font_size = 7) %>% #comment out if outputting html file
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped
  column_spec(4, width = "3em") %>% #wrap 'Effect Type' header 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. All ML2 meta-analyses with effect type 'r' except 'Moral foundations' and 'Social Value Orientation' were transformed to correlations from a variety of effect sizes. RP = Replication Project, K = no. primary studies, $\\\\hat\\\\tau$ = between studies standard deviation, CI = confidence intervals. Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large
heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/gtfjn/" ,
           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences"),
symbol = c("SMD effect size in Figure 3", "Log odds ratio effect size in Figure 3")) %>% landscape()
```

### 2020-03-27 code/05_figures-and-correlations.rmd
Made the heterogeneity estimates a little clearer for sole non-sig log odds ratio
Updated Figures to be APA consistent, minor table fix

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste("Average ", italic(I)^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  guides(color = guide_legend(override.aes = list(size = 1.4)))

@@

```{r Density-plot, fig.height=4, fig.width=6.47}
I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

@@

Figure 2. Simulated $I^2$  densities across 67 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 67 meta-analyses. Each simulated density consists of approximately 670,000 estimates.

@@

#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% #First compute meta-analytic results for all effects (will save: SMDs results)
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced

@@

log_odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or, rd_effects)) %>% 
  split(.$effect) %>% 
  map_dfr(log_or_fit, .id = "effect") #log_or_fit function is sourced

tau_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(log_odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(log_odds_ratios) %>% #add odds ratios
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
         eff_size = abs(eff_size), #need the absolute values for plotting
         tau = sqrt(tau2)) %>% 
  filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau plot----
tau_facet <- ggplot(tau_per_type, aes(x = eff_size, y = tau)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", italic(tau)))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

nrow(logOR[logOR$eff_size_p > 0.05,]) #only 1 log odds ratio not signifcant

>>>>

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type, linetype = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste("Average ", italic(I)^2," index", sep = "")),
                     minor_breaks = NULL) +
  scale_linetype_manual(name = "Effect type", 
                        values = c( "dotdash", "dotted", "solid", "dashed"),
                        breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
                        labels = c(expression(paste("Fisher's ", italic(z))),
                                   expression(paste("Cohen's ", italic(q))),
                                   expression(paste(italic(MD))),
                                   expression(paste(italic(SMD))))) + 
  scale_color_brewer(name = "Effect type", 
                     palette = "Dark2", 
                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
                     labels = c(expression(paste("Fisher's ", italic(z))),
                                   expression(paste("Cohen's ", italic(q))),
                                   expression(paste(italic(MD))),
                                   expression(paste(italic(SMD))))) +
  coord_cartesian(ylim = c(0, 100)) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  guides(color = guide_legend(override.aes = list(size = 1.2)))

@@

```{r Density-plot, fig.height=4, fig.width=6.47}
I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity)) + 
  geom_histogram(data = observed, aes(y = ..density.., x = I2, fill = Heterogeneity), bins = 100, alpha = 0.6)   +
  stat_density(geom="line", position="identity", #we use stat_density instead of geom_density to get only the density lines (and no fill)
               aes(linetype = Heterogeneity, color = Heterogeneity), size = 0.75)+ 
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
  scale_fill_manual(name = NULL, #drop legend title so that can place directly under other legend
                    values = "#666666", #fill color
                    breaks = "Observed",
                    labels = "Observed") +
  scale_color_manual(values = c("#D95F02", "#E6AB02", "#1B9E77","#E7298A"), #fill colors
                     breaks = c("Zero", "Small", "Medium", "Large"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
  theme(legend.position = c(0.85, 0.71), #placement of legend
        legend.spacing = unit(-0.4, "cm"), #move the two legends close to each other to seem like one
        legend.background = element_blank(), #remove legend background so that we can put a shared box around the two legends
        legend.box.background = element_rect(colour = "black")) + #create the shared box
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(I)^2," index", sep = ""))) +
  guides(linetype = guide_legend(order = 1),
         color  = guide_legend(order = 1))
#*****************

@@

Figure 2. Simulated $I^2$  densities across 68 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 68 meta-analyses. Each simulated density consists of approximately 680,000 estimates.

@@

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% 
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") %>% #MD_fit function is sourced
  mutate(effect_type = "Standardized Mean Difference")

@@

log_odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or, rd_effects)) %>% 
  split(.$effect) %>% 
  map_dfr(log_or_fit, .id = "effect") %>% #log_or_fit function is sourced
  mutate(effect_type = "Log Odds Ratio")

#combine into one dataframe for plotting
tau_per_type <- MD_standardized %>% 
  bind_rows(log_odds_ratios) %>% 
  mutate(eff_size = abs(eff_size), #need the absolute values for plotting
         tau = sqrt(tau2))

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau plot----
tau_facet <- ggplot(tau_per_type, aes(x = eff_size, y = tau)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", tau))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

logOR[logOR$eff_size_p > 0.05,] #only 1 log odds ratio not signifcant. tau = 0.13, I2 = 11.8, H2 = 1.05

### 2020-03-27 code/06_Supplement-tables-figures.Rmd
Updated Figures to be APA consistent, minor table fix

@@

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced

@@

**Note:** The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood. The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

>>>>

## Figure S1A

@@

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(outcomes1_2 == "mean _ SD") %>% 
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced

@@

**Note:** The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood. The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded. $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis. This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nonetheless. In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences. Effects reported as mean differences were standardized for the meta-analyses.

## Figure S1C

```{r plotC prep}

#Create plot labels
set.seed(499) #for the bootstrapping
all_effects_ci <- tau_per_type %>% 
  bootfitter_sigma2(.) #bootfitter is a sourced function

labels_all <- tau_per_type %>% #
  fitter_sigma2(.) %>% #fitter is a sourced function
  mutate(lab = paste0("r = ", r, " ", all_effects_ci$ci)) #put output into one variable for improved plotting

set.seed(500) #for the bootstrapping
restricted_effects_ci <- without_anchoring %>% 
  bootfitter_sigma2(.) #bootfitter is a sourced function

labels_restricted <- without_anchoring %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  fitter_sigma2(.) %>% #fitter is a sourced function
  mutate(lab = paste0("r = ", r, " ", restricted_effects_ci$ci)) #put output into one variable for improved plotting
```

```{r fig C}
within_plot_full <- ggplot(tau_per_type, aes(x = eff_size, y = s2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels_all[labels_all$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(s^2)))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid"))

without_anchoring_plot <- ggplot(without_anchoring, aes(x = eff_size, y = s2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels_restricted[labels_restricted$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(s^2)))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid"))

cowplot::plot_grid(within_plot_full, without_anchoring_plot, nrow = 2, labels = "AUTO")

ggsave("../figures/figure-S1C.png", dpi = 600, height =  7, width = 7)
```

Figure S1C. The Pearson correlation (_r_) between average absolute effect size and average within studies standard deviation for 40 effects that were measured as mean or standardized mean differences. Panel A shows results for all 40 effect sizes and panel B with the four largest (Anchoring 1 - 4) excluded. Effects reported as mean differences were standardized. Square brackets contain 95% bootstrapped percentile confidence intervals. 
```
